Social Feedback For Robotic Collaboration

### 2016-05-22 paper.tex

This work is primarily built off of \citet{eldon15thesis}, which describes a system for incremental speech and gesture recognition in an object-delivery domain. In previous work\citep{socialfeedback}, the model from \citet{eldon15thesis} is expanded from a bayesian inference model into a POMDP model that can ask yes-no questions. In this work, we generalize the idea of the affect of robot's actions on humans state within a POMDP framework.

Work demonstrating the importance of social feedback in human-human
communication has been done in the field of psycholinguistics. In  \cite{clark04}, one human (labeled the builder)
builds a Lego model according to instructions given by another human
(labeled the director). In the feedback-free trials, the director's
instructions were prerecorded, and the resulting models were very
inaccurate (in fact no model was completely correct). In the feedback
trials, errors were reduced by a factor of eight. Our goal is to
enable a robot to collaborate with a human in this way.

@@

@@

Markov Decision Processes (MDPs) are models that describe how an agent can take actions to transition between states, receiving rewards for its actions. Partially Observable Markov Decision Processes (POMDPs) are used to model MDPs where the true state is not known. Instead, the agent receives observations that are generated by the true state, and must infer what the true state is from the observations. Thus, the agent maintains a belief over true states which is updated as it receives new observations. In subsequent sections, we will refer to this belief over hidden states as $b$. The agent must then use this belief state to determine which action to take to maximize its expected value of the reward over time. This splits the POMDP into two main components, a state estimator and a policy generator. A typical graphical model for a POMDP is provided in figure~\ref{fig:pomdp}.
\tikzstyle{h} = [circle, draw, fill=white, minimum size=3em]
\tikzstyle{a} = [diamond, draw, fill=gray!40, minimum size=3em]
\tikzstyle{v} = [circle, draw, fill=gray!40, minimum size=3em]
\tikzstyle{line} = [draw, > = stealth, -latex]

@@

\tikzstyle{h} = [circle, draw, fill=white, minimum size=3em]
\tikzstyle{v} = [circle, draw, fill=gray!40, minimum size=3em]
\tikzstyle{line} = [draw, > = stealth, -latex]
\begin{figure}[H]
\begin{center}
	\begin{tikzpicture}[node distance = 1.5cm, auto]
		%actions
		\node [v] (ort) {$o_{t}$};
		\node [v, right of=ort] (oht) {$\omega_{\tau}$};
		\node [v, right of=oht] (ortp1) {$o_{t+1}$}; 
		\node [v, right of=ortp1] (ohtp1) {$\omega_{\tau+1}$}; 
		\node [v, left of=ort] (ohtm1) {$\omega_{\tau-1}$};
		\node [v, left of=ohtm1] (ortm1) {$o_{t-1}$};
		% states
		\node [h, above of=ort] (st) {$s_t$}; 
		\node [h, below of=oht] (sigmat) {$\sigma_\tau$};
		\node [h, above of=ortm1] (stm1) {$s_{t-1}$}; 
		\node [h, below of=ohtm1] (sigmatm1) {$\sigma_{\tau-1}$};
		\node [h, above of=ortp1] (stp1) {$s_{t+1}$}; 
		\node [h, below of=ohtp1] (sigmatp1) {$\sigma_{\tau+1}$};
		% edges; state -> obs
		\path [line] (st) edge (ort); 
		\path [line] (sigmat) edge (oht); 
		\path [line] (stm1) edge (ortm1); 
		\path [line] (sigmatm1) edge (ohtm1); 
		\path [line] (stp1) edge (ortp1); 
		\path [line] (sigmatp1) edge (ohtp1); 
		% state -> state
		\path [line] (stm1) edge (st); 
		\path [line] (st) edge (stp1); 
		\path [line] (sigmatm1) edge (sigmat); 
		\path [line] (sigmat) edge (sigmatp1); 
		% a -> state
		\path [line] (ortm1) edge (sigmatm1); 
		\path [line] (ort) edge (sigmat); 
		\path [line] (ortp1) edge (sigmatp1); 
		\path [line] (ohtm1) edge (st); 
		\path [line] (oht) edge (stp1); 
	\end{tikzpicture}
	\caption{A two-agent model based off two POMDPs}
	\label{fig:twoagent}
\end{center}
\end{figure}

>>>>

This work is primarily built off of \citet{eldon15thesis},\stnote{cite icra paper instead} which describes a system for incremental speech and gesture recognition in an object-delivery domain. In previous work\citep{socialfeedback}, the model from \citet{eldon15thesis} is expanded from a bayesian inference model into a POMDP model that can ask yes-no questions. In this work, we generalize the idea of the affect of robot's actions on humans state within a POMDP framework.

Work demonstrating the importance of social feedback in human-human
communication has been done in the field of psycholinguistics. In  \citet{clark04}, one human (labeled the builder)
builds a Lego model according to instructions given by another human
(labeled the director). In the feedback-free trials, the director's
instructions were prerecorded, and the resulting models were very
inaccurate (in fact no model was completely correct). In the feedback
trials, errors were reduced by a factor of eight. Our goal is to
enable a robot to collaborate with a human in this way.

@@

\stnote{Put a few sentences here giving an overview.  no section/subsection without intro text}

@@

Markov Decision Processes (MDPs) are models that describe how an agent can take actions to transition between states, receiving rewards for its actions. Partially Observable Markov Decision Processes (POMDPs) are used to model MDPs where the true state is not known. Instead, the agent receives observations that are generated by the true state, and must infer what the true state is from the observations. Thus, the agent maintains a belief over true states which is updated as it receives new observations. In subsequent sections, we will refer to this belief over hidden states as $b$. The agent must then use this belief state to determine which action to take to maximize its expected value of the reward over time. This splits the POMDP into two main components, a state estimator and a policy generator. A typical graphical model for a POMDP is provided in figure~\ref{fig:pomdp}.\stnote{cut this figure}

\tikzstyle{h} = [circle, draw, fill=white, minimum size=3em]
\tikzstyle{a} = [diamond, draw, fill=gray!40, minimum size=3em]
\tikzstyle{v} = [circle, draw, fill=gray!40, minimum size=3em]
\tikzstyle{line} = [draw, > = stealth, -latex]

@@

\tikzstyle{h} = [circle, draw, fill=white, minimum size=3em]
\tikzstyle{v} = [circle, draw, fill=gray!40, minimum size=3em]
\tikzstyle{line} = [draw, > = stealth, -latex]
\begin{figure}[H]
\begin{center}
	\begin{tikzpicture}[node distance = 1.5cm, auto]
		%actions
		\node [v] (ort) {$o_{t}$};
		\node [v, right of=ort] (oht) {$\omega_{\tau}$};
		\node [v, right of=oht] (ortp1) {$o_{t+1}$}; 
		\node [v, right of=ortp1] (ohtp1) {$\omega_{\tau+1}$}; 
		\node [v, left of=ort] (ohtm1) {$\omega_{\tau-1}$};
		\node [v, left of=ohtm1] (ortm1) {$o_{t-1}$};
		% states
		\node [h, above of=ort] (st) {$s_t$}; 
		\node [h, below of=oht] (sigmat) {$\sigma_\tau$};
		\node [h, above of=ortm1] (stm1) {$s_{t-1}$}; 
		\node [h, below of=ohtm1] (sigmatm1) {$\sigma_{\tau-1}$};
		\node [h, above of=ortp1] (stp1) {$s_{t+1}$}; 
		\node [h, below of=ohtp1] (sigmatp1) {$\sigma_{\tau+1}$};
		% edges; state -> obs
		\path [line] (st) edge (ort); 
		\path [line] (sigmat) edge (oht); 
		\path [line] (stm1) edge (ortm1); 
		\path [line] (sigmatm1) edge (ohtm1); 
		\path [line] (stp1) edge (ortp1); 
		\path [line] (sigmatp1) edge (ohtp1); 
		% state -> state
		\path [line] (stm1) edge (st); 
		\path [line] (st) edge (stp1); 
		\path [line] (sigmatm1) edge (sigmat); 
		\path [line] (sigmat) edge (sigmatp1); 
		% a -> state
		\path [line] (ortm1) edge (sigmatm1); 
		\path [line] (ort) edge (sigmat); 
		\path [line] (ortp1) edge (sigmatp1); 
		\path [line] (ohtm1) edge (st); 
		\path [line] (oht) edge (stp1); 
	\end{tikzpicture}
	\caption{A two-agent model based off two POMDPs \stnote{Let's name this model and call it our model.}}
	\label{fig:twoagent}
\end{center}
\end{figure}
